This work demonstrates the feasibility and effectiveness of integrating Fully Homomorphic Encryption into mobile applications using our Fully Homomorphic Encryption Library plugin, written in Dart. By leveraging Microsoft SEAL, our implementation enables high-performance encrypted computations on mobile devices, meeting critical privacy and security demands without compromising user experience.

Through our Distance Measure plugin, we achieved consistent and accurate similarity detection scores between videos using Kullback-Leibler Divergence (KLD), Bhattacharyya Coefficient, and Cramer’s Distance. Our results reveal that both Cramer Distance and Bhattacharyya Coefficient exhibit lower noise accumulation compared to KLD, underscoring the importance of distance measure selection based on computational requirements and noise sensitivity. The reduced variance in our Dart implementation compared to the Python baseline further highlights its stability and reliability for mobile applications. The advancements within SEAL v4.1 have contributed significantly to our system’s performance. However, the pre-processing library, OpenCV, has negatively impacted the performance of video processing and feature extraction compared to FFmpeg.

Ultimately, this project lays the foundation for future applications of FHE in mobile environments, especially in fields like healthcare and secure data exchange, where privacy and accuracy are paramount. By making SEAL accessible within a mobile-compatible, modular framework, we are opening pathways for broader adoption of FHE and setting the stage for innovation in mobile security.
