\begin{glossary}
\item[Fully Homomorphic Encryption (FHE)] A type of encryption that allows computations to be performed on encrypted data without needing to decrypt it, ensuring data privacy throughout the processing.

\item[Cheon-Kim-Kim-Song (CKKS) Scheme] A fully homomorphic encryption scheme that supports approximate arithmetic on real numbers, particularly useful for decimal-based computations.

\item[Microsoft Simple Encrypted Arithmetic Library (SEAL)] An open-source library developed by Microsoft for implementing homomorphic encryption, supporting arithmetic operations on encrypted data.

\item[Kullback-Leibler Divergence (KLD)] A measure of how one probability distribution diverges from a second, reference probability distribution, used in similarity analysis.

\item[Bhattacharyya Coefficient (BC)] A similarity measure that quantifies the amount of overlap between two probability distributions, commonly used in pattern recognition.

\item[Cramer's Distance (CD)] A statistical measure used to quantify dissimilarity between two probability distributions, sensitive to sample size.

\item[Probability Distribution Form (PDF)] A method of representing data where each value indicates the relative frequency of occurrences, used here to represent video frames for similarity analysis.

\item[Cumulative Distribution Form (CDF)] A representation of a probability distribution where each value is the cumulative sum of probabilities up to that point, ensuring the last value is equal to one. Used in similarity analysis for comparing probability distributions.

\item[Flutter] An open-source, cross-platform framework by Google for building natively compiled applications for mobile, web, and desktop from a single codebase.

\item[Dart] A programming language optimized for building fast applications on any platform, used in the development of Flutter apps.

\item[Foreign Function Interface (FFI)] A Dart feature that allows interaction with C libraries, enabling functionalities like encrypted computations within the Dart and Flutter ecosystems.

\item[FFmpeg] A multimedia framework commonly used for video and audio processing, used here for video preprocessing in mobile applications.

\item[OpenCV] An open-source computer vision and machine learning software library that provides tools for image and video processing.

\item[Conan] A dependency management tool used for packaging and managing C++ libraries, facilitating cross-compilation for various platforms.

\item[GitHub Actions] A CI/CD tool that automates tasks such as building, testing, and deploying software, supporting the automation of plugin testing and deployment in this project.

\end{glossary}
