%  ========================================================================
%  Copyright (c) 1985 The University of Washington
%
%  Licensed under the Apache License, Version 2.0 (the "License");
%  you may not use this file except in compliance with the License.
%  You may obtain a copy of the License at
%
%      http://www.apache.org/licenses/LICENSE-2.0
%
%  Unless required by applicable law or agreed to in writing, software
%  distributed under the License is distributed on an "AS IS" BASIS,
%  WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
%  See the License for the specific language governing permissions and
%  limitations under the License.
%  ========================================================================
%

% Documentation for University of Washington thesis LaTeX document class
% by Jim Fox
% fox@washington.edu
%
%    Revised 2020/02/24, added \caption()[]{} option.  No ToC.
%
%    Revised for version 2015/03/03 of uwthesis.cls
%    Revised, 2016/11/22, for cleanup of sample copyright and title pages
%
%    This document is contained in a single file ONLY because
%    I wanted to be able to distribute it easily.  A real thesis ought
%    to be contained on many files (e.g., one for each chapter, at least).
%
%    To help you identify the files and sections in this large file
%    I use the string '==========' to identify new files.
%
%    To help you ignore the unusual things I do with this sample document
%    I try to use the notation
%       
%    % --- sample stuff only -----
%    special stuff for my document, but you don't need it in your thesis
%    % --- end-of-sample-stuff ---


%    Printed in twoside style now that that's allowed
%
 
\documentclass [11pt, proquest] {uwthesis}[2020/02/24]
 
%
% The following line would print the thesis in a postscript font 

% \usepackage{natbib}
% \def\bibpreamble{\protect\addcontentsline{toc}{chapter}{Bibliography}}

\setcounter{tocdepth}{1}  % Print the chapter and sections to the toc
 

% ==========   Local defs and mods
%

% --- sample stuff only -----
% These format the sample code in this document

\usepackage{alltt}  % 
\newenvironment{demo}
  {\begin{alltt}\leftskip3em
     \def\\{\ttfamily\char`\\}%
     \def\{{\ttfamily\char`\{}%
     \def\}{\ttfamily\char`\}}}
  {\end{alltt}}
 
% metafont font.  If logo not available, use the second form
%
% \font\mffont=logosl10 scaled\magstep1
\let\mffont=\sf
% --- end-of-sample-stuff ---

% Table 5.1
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{array}

% BibTeX
\usepackage{url}

\begin{document}
 
% ==========   Preliminary pages
%
% ( revised 2012 for electronic submission )
%

\prelimpages
 
%
% ----- copyright and title pages
%
\Title{GhostPeerShare}
\Author{Jeffrey Murray Jr}
\Year{2024}
\Program{Cybersecurity Engineering}

\Chair{Brent Lagesse}{Dr.}{Computing \& Software Systems}
\Signature{Geethapriya Thamilarasu}
\Signature{Yang Peng}

\copyrightpage

\titlepage  

 
%
% ----- signature and quoteslip are gone
%

%
% ----- abstract
%


\setcounter{page}{-1}
\input{abstract}
 
%
% ----- contents & etc.
%
\tableofcontents
\listoffigures
\listoftables
 
%
% ----- glossary 
%
\chapter*{Glossary}      % starred form omits the `chapter x'
\addcontentsline{toc}{chapter}{Glossary}
\thispagestyle{plain}
%
\input{glossary}
 
%
% ----- acknowledgments
%
% \acknowledgments{% \vskip2pc
%   % {\narrower\noindent
%   The author wishes to express sincere appreciation to
%   University of Washington, where he has had the opportunity
%   to work with the \TeX\ formatting system,
%   and to the author of \TeX, Donald Knuth, {\it il miglior fabbro}.
%   % \par}
% }

%
% end of the preliminary pages

%
% ==========      Text pages
%

\textpages
 
% ========== Chapter 1
 
\chapter {Introduction}

This chapter outlines the challenges and limitations of Microsoft's Simple Encrypted Arithmetic Library. Next, we identify beneficiaries and major stakeholders within the Fully Homomorphic Encryption (FHE) domain. Finally, we present a modular interface that grants access to FHE functionality on modern mobile applications.

\input{1 Introduction/1.1 Problem Statement}
\input{1 Introduction/1.2 Stakeholders}
\input{1 Introduction/1.3 Contributions}

% ========== Chapter 2
 
\chapter{Background}

This section outlines the technologies and methods used in this research. We start with Flutter, an open-source framework for building cross-platform applications, and highlight its benefits for mobile development. Next, we introduce the Simple Encrypted Arithmetic Library and explain the process of performing computations on encrypted data. Finally, we discuss the distance measures used for privacy-preserving video similarity analysis, focusing on Kullback-Leibler Divergence, Bhattacharyya Coefficient, and Cramer’s Distance. We examine the properties and uses of each metric to show their importance in our work.

\input{2 Background/2.1 Flutter}
\input{2 Background/2.2 SEAL}
\input{2 Background/2.3 Distance Measures}

% ========== Chapter 3
 
\chapter{Related Work}

This section reviews significant advancements in Fully Homomorphic Encryption (FHE) and related methodologies relevant to this project. We begin with an overview of existing FHE libraries. Next, we examine the Proof of Presence Share methodology, an innovative application of FHE to compute video similarity. Finally, we discuss alternative video similarity measures.

\input{3 Related Work/3.1 FHE Libraries}
\input{3 Related Work/3.2 Pop-Share}
\input{3 Related Work/3.3 Video Similarity}

% ========== Chapter 4
 
\chapter{Design}

The core design principle is modularity, with each component designed to support additional cryptographic libraries and be flexible for future applications. The implementation includes three core components: two Dart plugins and a Flutter application. The Fully Homomorphic Encryption (FHE) Library plugin integrates Microsoft SEAL and delivers FHE arithmetic for the Dart and Flutter communities. The Distance Measure plugin implements Kullback-Leibler Divergence, Cramer Distance, and the Bhattacharyya Coefficient, along with simplified versions of their original algorithms developed for basic FHE arithmetic operations. GhostPeerShare relies on both Dart plugins as a Flutter-based peer-to-peer Pop-Share application. It enables secure video exchange with strong privacy guarantees.

\input{4 Design/4.1 FHE Plugin}
\input{4 Design/4.2 Distance Measure}
\input{4 Design/4.3 Video Similarity App}

% ========== Chapter 5

\chapter{Results}

In this section, we compare our implementation to the foundational contributions of SSO and Pop-Share. In order to evaluate the accuracy of Fully Homomorphic Encryption Library plugin in Dart, we measure the amount of noise generated during encrypted operations. Next, we compare our implementation of our distance measures using the original pre-processed video frames from SSO. Next, we compare the same video from various angles and determine the accuracy of our implementation. Next, we compare the distance measures for similar scenes against different scenes. Finally, we compare the performance across multiple linux and android devices.

\input{5 Results/5.1 Noise Accumulation}
\input{5 Results/5.2 Pop-Share Distance Measure}
\input{5 Results/5.3 Field of View}
\input{5 Results/5.4 Scene Distance Measure}
\input{5 Results/5.5 Performance}

% ========== Chapter 6

\chapter{Conclusion}
\input{conclusion}

%
% ==========   Bibliography
%
\nocite{*}   % include everything in the uwthesis.bib file
\bibliographystyle{ieeetr}
\bibliography{uwthesis}
%
% ==========   Appendices
%
\appendix
\raggedbottom\sloppy
 
% ========== Appendix A
 
\chapter{Tables}
 
\input{Appendix/ANN Trials}

\end{document}
